%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {EMBL-EBI} % Organization
    {Cambridge, UK} % Location
    {Aug. 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on an internal application for processing huge amount of Protein data in health.}
        \item {Working on several open source web components.}
        \item {Lead engineer on an internal application.}
        \item {Redesigned user interface and improved user experience by introducing material design.}
        \item {Introduced code reviews and improved code quality by 30i\%.}
        \item {Tech stack: Java, Javascript, Spring, Angular, React.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Google (Consultant software engineer)} % Organization
    {Gurgaon, India} % Location
    {Mar. 2013 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on an ad platform integration project.}
        \item {Designed, developed and shipped the project in expected time frame.}
        \item {Worked closely with a team of 8-10 on a Google business integration tool.}
        \item {Worked on a number of reusable UI components.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelance Python Developer} % Job title
    {SARL SYNERGY} % Organization
    {Delhi, India} % Location
    {Mar. 2012 - Jan. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project: ERP for an insurance company - implemented the accounting, contract management, commission management and claim management followed by their website integration.}
        \item {Project: ERP for a furniture distribution company - implemented accounting, sale management and with strong needs in stock management and cost control and synchronized with their e-commerce Magento system through the OpenERP-Magento connector.}
        \item {Project: ERP for a start-up of photo management - implemented accounting, sale management and also photo management followed by their website integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Associate} % Job title
    {ENova Technologies Pvt. Ltd.} % Organization
    {Delhi, India} % Location
    {Jun. 2011 - Jan. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented accounting, sales management and stock management for a number of clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
